### 2009-07-08 docs/architecture/architecture.tex
describe the MAESTRO directory structure

>>>>

All the files needed to build MAESTRO are contained in the {\tt
fParallel} directory structure.  Briefly, the sub-directories
are:
\begin{itemize}
\item {\tt boxlib/}

 boxlib is a library for describing meshes consisting of a union
 of boxes.  The boxlib modules define the basic datatypes used
 in MAESTRO.

\item {\tt data\_processing/}

 Simple Fortran-based analysis routines (e.g.\ extract a line from a
 multidimensional dataset) that operate on boxlib plotfiles.

\item {\tt doc/}

 Documentation describing the basic algorithm.

\item {\tt extern/}

 External modules, like ODE integrators, equations of state, reaction
 networks

\item {\tt MAESTRO/}

 The main MAESTRO algorithm files.  Here you will find the main driver,
 the advection routines, etc.

 Important directories under {\tt MAESTRO/} include:

 \begin{itemize}

 \item {\tt initial\_models}

   Several sub-directories containing routines to generate
   1D initial conditions in hydrostatic equilibrium for 
   mapping onto the MAESTRO grid.

 \item problem directories: {\tt test}, {\tt test2}, {\tt
   test\_spherical}, $\ldots$

   Each problem in MAESTRO gets it own subdirectory.  The {\tt
   GNUmakefile} includes the instructions on how to build the
   executable, including what modules in {\tt extern} are used.

   Any file that you place in a sub-directory here takes 
   precedence over a file of the same name in {\tt MAESTRO/}.
   This allows problems to have custom versions of the main
   MAESTRO routines (e.g.\ initial conditions via {\tt initdata.f90}.

 \end{itemize}

\item {\tt mg/}

  The multigrid solver.

\item {\tt mk/}

  The generic Makefiles that store the compilation flags for
  various platforms.

\item {\tt scripts/}

  Some simple scripts that are useful for building, running,
  maintaining MAESTRO.

\end{itemize}
